---
title: "p8105_hw1_yc4584"
author: "Yingyu Cui"
date: "2024-09-17"
output: github_document
---

# Problem 1

- now load the penguins dataset from the palmerpenguins package
```{r load data}
data("penguins", package = "palmerpenguins")
```

This is a short discription for the dataset:

- the dataset includes following variables: `r names(penguins)`.

  the dataset includes `r nrow(penguins)` rows and `r ncol(penguins)` columns.

  the mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`mm.
  
  
This is the scatterplot of flipper_length_mm (y) vs bill_length_mm (x).
```{r scatterplot, warning=FALSE, message=FALSE}
library(ggplot2)
scatterplot = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(
    title = "Scatterplot of Flipper and Bill Length",
    x = "bill_length_mm",
    y = "flipper_length_mm",
    color = "species"
  )
print(scatterplot)
ggsave(filename = "Scatterplot of Flipper and Bill Length.png", plot = scatterplot)
```




